Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-15 paper/zhang-cook-laa-langrene-menendez.Rmd
list functions in ferrn in  implementation section

- \code{explore\_trace\_search()}: produces summary plots, as shown in Figure \ref{fig:toy-search}
- \code{explore\_trace\_interp()}: produces trace plots for the interpolation points, as shown in Figure \ref{fig:toy-interp}
- \code{explore\_space\_pca()}: produces plots of projection basis on the reduced space by PCA, as shown in Figure \ref{fig:toy-pca}. Animated version in Figure \ref{fig:toy-pca-animated} can be turned on via the argument `animate = TRUE`
- \code{explore\_space\_tour()}: produces animated tour view on the full space of the projection bases, as shown in Figure \ref{fig:toy-tour}.

- \code{get\_*()} extracts and manipulates certain components from the existing data object.
  - \code{get\_best()}: extracts the best basis found in the data object
  - \code{get\_start()}: extracts the starting basis
  - \code{get\_interp()}: extracts the observations in the interpolation
  - \code{get\_search\_count()}: produces the summary table of the number of observation in each iteration
  - \code{get\_basis\_matrix()}: flattens all the bases into a matrix

- \code{bind\_*()} incorporates additional information outside the tour optimisation into the data object.
  - \code{bind\_theoretical()}: incorporates the best possible basis to the existing data object with the supply of the index function and original data for producing the index value. 
  - \code{bind\_random()}: generates 1000 points on the high dimensional surface of a sphere and binds it to the existing data object and output as a tibble object. `bind_random_matrix()` binds the points to the basis matrix.

- Color
  - \code{botanical\_palettes}: a collection of color palettes from Australian native plants. Quantitative palettes include daisy, banksia and cherry and sequential palettes contain fern and acacia.
  - \code{botanical\_pal()}: a color interpolator 
  - \code{scale\_color\_botanical()}: a ggplot construction for using botanical palettes.

>>>>

- Main plotting functions:

  - \code{explore\_trace\_search()} produces summary plots, as shown in Figure \ref{fig:toy-search}
  - \code{explore\_trace\_interp()}produces trace plots for the interpolation points, as shown in Figure \ref{fig:toy-interp}
  - \code{explore\_space\_pca()} produces plots of projection basis on the reduced space by PCA, as shown in Figure \ref{fig:toy-pca}. Animated version in Figure \ref{fig:toy-pca-animated} can be turned on via the argument `animate = TRUE`
  - \code{explore\_space\_tour()} produces animated tour view on the full space of the projection bases, as shown in Figure \ref{fig:toy-tour}.

- \code{get\_*()} extracts and manipulates certain components from the existing data object.
  - \code{get\_best()} extracts the best basis found in the data object
  - \code{get\_start()} extracts the starting basis
  - \code{get\_interp()} extracts the observations in the interpolation
  - \code{get\_interp\_last()} extracts the end observations of the interpolation in each iteration
  - \code{get\_anchor()} extracts the target observations found by the optimiser
  - \code{get\_search()} extracts the search observations evaluated by the optimiser
  - \code{get\_search\_count()} produces the summary table of the number of observation in each iteration
  - \code{get\_center()} produces the center point of the basis space estimated by the starting points
  - \code{get\_space\_param()} produces the coordinates of the center and radius of the basis space
  - \code{get\_theo()} extracts the theoretical observations from the data object
  - \code{get\_interrupt()} extract the end point of the interpolation and the target point when an interruption happens
  - \code{get\_basis\_matrix()}: flattens all the bases into a matrix

- \code{bind\_*()} incorporates additional information outside the tour optimisation into the data object.
  - \code{bind\_theoretical()} incorporates the best possible basis to the existing data object with the supply of the index function and original data for producing the index value. 
  - \code{bind\_random()} generates 1000 points on the high dimensional surface of a sphere and binds it to the existing data object and output as a tibble object. 
  - \code{bind\_random\_matrix()} binds the points to the basis matrix.

- Utilities
  - \code{add\_*()} are internal wrapper functions that facilitate the composition of PCA plot
  - \code{theme\_fern()} and \code{format\_label()} for better display of the grid lines and axis formatting
  - \code{clean\_method()} for clean up the name of the optimisers
  - \code{botanical\_palettes} is a collection of color palettes from Australian native plants. Quantitative palettes include daisy, banksia and cherry and sequential palettes contain fern and acacia.
  - \code{botanical\_pal()} as the color interpolator 
  - \code{scale\_color\_botanical()} is a ggplot2 scale for botanical palettes.

### 2021-01-15 paper/zhang-cook-laa-langrene-menendez.tex
list functions in ferrn in  implementation section

\begin{itemize}
\item
  \code{explore\_trace\_search()}: produces summary plots, as shown in
  Figure \ref{fig:toy-search}
\item
  \code{explore\_trace\_interp()}: produces trace plots for the
  interpolation points, as shown in Figure \ref{fig:toy-interp}
\item
  \code{explore\_space\_pca()}: produces plots of projection basis on
  the reduced space by PCA, as shown in Figure \ref{fig:toy-pca}.
  Animated version in Figure \ref{fig:toy-pca-animated} can be turned on
  via the argument \texttt{animate\ =\ TRUE}
\item
  \code{explore\_space\_tour()}: produces animated tour view on the full
  space of the projection bases, as shown in Figure \ref{fig:toy-tour}.
\item
  \code{get\_*()} extracts and manipulates certain components from the
  existing data object.

  \begin{itemize}
  \tightlist
  \item
    \code{get\_best()}: extracts the best basis found in the data object
  \item
    \code{get\_start()}: extracts the starting basis
  \item
    \code{get\_interp()}: extracts the observations in the interpolation
  \item
    \code{get\_search\_count()}: produces the summary table of the
    number of observation in each iteration
  \item
    \code{get\_basis\_matrix()}: flattens all the bases into a matrix
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

  \begin{itemize}
  \tightlist
  \item
    \code{bind\_theoretical()}: incorporates the best possible basis to
    the existing data object with the supply of the index function and
    original data for producing the index value.
  \item
    \code{bind\_random()}: generates 1000 points on the high dimensional
    surface of a sphere and binds it to the existing data object and
    output as a tibble object. \texttt{bind\_random\_matrix()} binds the
    points to the basis matrix.
  \end{itemize}
\item
  Color

  \begin{itemize}
  \tightlist
  \item
    \code{botanical\_palettes}: a collection of color palettes from
    Australian native plants. Quantitative palettes include daisy,
    banksia and cherry and sequential palettes contain fern and acacia.
  \item
    \code{botanical\_pal()}: a color interpolator
  \item
    \code{scale\_color\_botanical()}: a ggplot construction for using
    botanical palettes.
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item
  Main plotting functions:

  \begin{itemize}
  \tightlist
  \item
    \code{explore\_trace\_search()} produces summary plots, as shown in
    Figure \ref{fig:toy-search}
  \item
    \code{explore\_trace\_interp()}produces trace plots for the
    interpolation points, as shown in Figure \ref{fig:toy-interp}
  \item
    \code{explore\_space\_pca()} produces plots of projection basis on
    the reduced space by PCA, as shown in Figure \ref{fig:toy-pca}.
    Animated version in Figure \ref{fig:toy-pca-animated} can be turned
    on via the argument \texttt{animate\ =\ TRUE}
  \item
    \code{explore\_space\_tour()} produces animated tour view on the
    full space of the projection bases, as shown in Figure
    \ref{fig:toy-tour}.
  \end{itemize}
\item
  \code{get\_*()} extracts and manipulates certain components from the
  existing data object.

  \begin{itemize}
  \tightlist
  \item
    \code{get\_best()} extracts the best basis found in the data object
  \item
    \code{get\_start()} extracts the starting basis
  \item
    \code{get\_interp()} extracts the observations in the interpolation
  \item
    \code{get\_interp\_last()} extracts the end observations of the
    interpolation in each iteration
  \item
    \code{get\_anchor()} extracts the target observations found by the
    optimiser
  \item
    \code{get\_search()} extracts the search observations evaluated by
    the optimiser
  \item
    \code{get\_search\_count()} produces the summary table of the number
    of observation in each iteration
  \item
    \code{get\_center()} produces the center point of the basis space
    estimated by the starting points
  \item
    \code{get\_space\_param()} produces the coordinates of the center
    and radius of the basis space
  \item
    \code{get\_theo()} extracts the theoretical observations from the
    data object
  \item
    \code{get\_interrupt()} extract the end point of the interpolation
    and the target point when an interruption happens
  \item
    \code{get\_basis\_matrix()}: flattens all the bases into a matrix
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

  \begin{itemize}
  \tightlist
  \item
    \code{bind\_theoretical()} incorporates the best possible basis to
    the existing data object with the supply of the index function and
    original data for producing the index value.
  \item
    \code{bind\_random()} generates 1000 points on the high dimensional
    surface of a sphere and binds it to the existing data object and
    output as a tibble object.
  \item
    \code{bind\_random\_matrix()} binds the points to the basis matrix.
  \end{itemize}
\item
  Utilities

  \begin{itemize}
  \tightlist
  \item
    \code{add\_*()} are internal wrapper functions that facilitate the
    composition of PCA plot
  \item
    \code{theme\_fern()} and \code{format\_label()} for better display
    of the grid lines and axis formatting
  \item
    \code{clean\_method()} for clean up the name of the optimisers
  \item
    \code{botanical\_palettes} is a collection of color palettes from
    Australian native plants. Quantitative palettes include daisy,
    banksia and cherry and sequential palettes contain fern and acacia.
  \item
    \code{botanical\_pal()} as the color interpolator
  \item
    \code{scale\_color\_botanical()} is a ggplot2 scale for botanical
    palettes.
  \end{itemize}
\end{itemize}
